Considering scale in multilayer animal social networks

### 2020-06-22 paper/manuscript.Rmd
fin hab p

<!-- habitat+social -->
Social structure and habitat selection are intimately related: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. 
Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, the
(3) habitat patches within the home range and (4) specific resources within a
habitat patch. <!--Kie et al. [-@Kie_2002] found that, independently, third order of
selection was insufficient for capturing landscape attributes selected for by
mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.-->
Moving past this hierarchical perspective, Mayor (2007) emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to be associated with
certain behaviours.

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
social network graph strength differed between seasons, where 
graph strength was stronger in winter and contrastingly low in summer when
resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
bison*) showed stronger habitat selection in larger groups, and avoidance of
predation risk was a main factor contributing to their habitat selection
[@Fortin_2009]. These examples, comparing sociality and habitat selection across
temporal or spatial contexts, are implicitly multilayer analyses.

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of habitat spatial
resolution on multilayer network metrics. <!--The results indicate varied influence
of increasing spatial resolution depending on the habitat layer.--> As spatial
resolution increased, edge overlap decreased in foraging habitats while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Foraging is a rare (14.5% of the landscape) and
patchy habitat on Fogo Island and the proportion of relocations in foraging habitat
type decreased as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Similar to increasing social distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Foraging and open
layers had greater individual variation in graph strength, while foraging was the
only layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.

>>>>

<!-- habitat+social -->
Social structure and habitat selection are intimately related: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, the (3) habitat patches within the home range and
(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
that, independently, third order of selection was insufficient for capturing
landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
scale larger than their home range size. Moving past this hierarchical
perspective, Mayor (2007) emphasized the importance of considering a broad
continuum of scales to reveal scale-dependent selection and avoid the bias of
predefined scales assumed to be associated with certain behaviours.

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
social network graph strength was higher in winter and contrastingly lower in summer when
resource availability is more homogeneous [@Peignier_2019]. Bison (*Bison
bison*) showed stronger habitat selection in larger groups, and avoidance of
predation risk was a main factor contributing to their habitat selection
[@Fortin_2009]. These examples, comparing sociality and habitat selection across
spatial and temporal contexts, are implicitly multilayer analyses.

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat type as in
Figure \@ref(fig:lcres). Since habitat data are available across a range of
spatial scales, we evaluated the influence of increasing spatial resolution on
multilayer network metrics. As spatial resolution increased, edge overlap
remained stable in open and forest layers but decreased in foraging layers
(Figure \@ref(fig:socres) D). Graph strength did not change in
forest layers with increasing spatial resolution (Figure \@ref(fig:socres) E).
Foraging and open layer had greater individual variation in graph strength, and
foraging layers showed an increase in graph strength with increasing spatial
resolution (Figure \@ref(fig:socres) E). Foraging habitat is rare (14.5% of the
landscape) on Fogo Island and the proportion of relocations in foraging habitat
decreased as spatial resolution increased (14.5% at 30 m - <2% at 1000 m).
Despite this, at 30 m resolution the foraging layer had similar edge overlap as
the open layer indicating its importance in caribou sociality. As such,
multilayer network measures related to habitat are explicitly dependent on
spatial scale.  If the spatial resolution of the habitat data are insufficient
to capture rare habitats, for example, context-specific relationships between
individuals may not be captured.
